Reduced growth due to belowground sink limitation is not fully explained by reduced photosynthesis

### 2017-02-06 manuscript/editor_response_tree_physiology.Rmd
editor comments reviews

- *Comment: 1. It seems that there are two different effects: rooting volume and container/free rooting. And it seems that the latter is dominating and the clear relations with rooting volume are often missing... ignoring this later treatment may depply change your way of interpreting the results*

@@

\
*Response*: 
We have removed the statement "Leaf respiration is included in the calculation of *P*." and added a suffice description of how dark respiration was calculated for each 15 minute interval to then caluclate *A*~n~.

@@

@@

@@

\
*Response*: This is entirely true and was overlooked by the authors.  This statement has been removed from the results section. Perhaps this provides additionally evidence of how A and G can become decoupled under sink manipulation.

@@

\
*Response*: 
\
- *Comment: 22. L443: again, what is An? And please show us the evidence of a sink limitation on An of seedlings in container. There is not so much effect of container size on leaf photosynthetic parameter in Table 3*

@@

\
*Response*: 
\
- *Comment: 24. L477: It is not true that “increases in specific root length were detected in several of the soil volume treatments” It is detected in only one, and not in the smallest one.*

\
*Response*: We have corrected this statment in the discussion to more accurately reflect the observed results.
\
- *Comment: 25. L483: There is no reduction in leaf photosynthesis due to the restricted soil volume, according to the data you reported in Table 3. Make clear what is leaf An. The reduction in whole plant assimilation may mainly be due to a reduction in plant leaf area, which in fact is only evident for the largest soil volume. Final plant leaf area can be added in table 1 with stats. It will be helpful as it is not so easy to visualize differences on figure 1.*

\
*Response*: 
\
- *Comment: 26. L477: L483-484: I disagree that reductions in Amax and biomass were strongly correlated. The correlation is driven by high value of the free soil. R2 will drop from 0.88 to 0.32 if you remove this last treatment.*

>>>>

- *Comment: 1. It seems that there are two different effects: rooting volume and container/free rooting. And it seems that the latter is dominating and the clear relations with rooting volume are often missing... ignoring this later treatment may depply change your way of interpreting the results. Even the stats are strongly influenced by this treatment (effect on residual error for example).*

\
*Response*: We agree with the editor's comments that the effects of soil volume have not been properly accounted for in several places in the manuscript. Particularly in the discussion we have clarified the nature of the effect type, where soil volume effects have often been over-emphasized. We agree that the stats are strongly influenced by the Free seedling, but this is also representative of the observed effects of root restirction on *A*~sat~, TNC and leaf N across all containers throughout all measurement campaigns. As the impacts of root restriction and poor quality soil impacted were evident across all treatments 
We feel that addressing individual effects of specific volume treatments, or combining soil volume treament effects, would overly complicate the paper and would not improve our intrepretation of the results.

@@

\
*Response*: The editor makes several good points here. We have re-written the equation to better descibe the way daily total leaf net C gain (*P*~day~) was calculated. We have also removed the statement "Leaf respiration is included in the calculation of *P*." and added a accurate description of how the area based respiration component was calculated at each 15 minute interval to then model leaf level net photosynthesis rates.

@@

\
*Response*: We agree with each of the editors points here.  With a comment #6 we have now clearly defined the "total net leaf C gain term".  As the edigor points out there are several places where leaf *A*~n~ is discussed inappropriately, especially in the discussion.  Throughout the manuscript we have revised use of terms for C gain to accurately reflect either measured photosynthesis rates (*A*~sat~), leaf level rates of net photosynthesis (*A*~n~) or modelled cumulative total net leaf C gain (*P*~day~).

@@

\
*Response*: editorial change made.

@@

\
*Response*: This point was overlooked by the authors. This statement has been removed from the results section.

@@

*Response*: We agree with the editor's comments.  There is convincing evidence that nutrient uptake was negatively affected in this experiment but the mechanism is yet unidentified.  Understanding the processes by which belowground sink manipulation manifests belowground will be important for future expereiments using local soils. We hope that this dataset and experimental design can aid in future experiments to further investigate belowground sink limitation.

\
- *Comment: 22. L443: again, what is An? And please show us the evidence of a sink limitation on An of seedlings in container. There is not so much effect of container size on leaf photosynthetic parameter in Table 3*

@@

\
- *Comment: 24. L477: It is not true that “increases in specific root length were detected in several of the soil volume treatments” It is detected in only one, and not in the smallest one.*

\
*Response*: We have corrected this statment in the discussion to more accurately reflect the observed results.

- *Comment: 25. L483: There is no reduction in leaf photosynthesis due to the restricted soil volume, according to the data you reported in Table 3. Make clear what is leaf An. The reduction in whole plant assimilation may mainly be due to a reduction in plant leaf area, which in fact is only evident for the largest soil volume. Final plant leaf area can be added in table 1 with stats. It will be helpful as it is not so easy to visualize differences on figure 1.*

\
*Response*: We have added both measured *A*~sat~ and harvested leaf area into Table 1 and 3, respectively.  Both of *A*~sat~ and leaf area were significantly reduced in containers from the free seedlings.

\
- *Comment: 26. L477: L483-484: I disagree that reductions in Amax and biomass were strongly correlated. The correlation is driven by high value of the free soil. R2 will drop from 0.88 to 0.32 if you remove this last treatment.*

### 2017-02-06 manuscript/manuscript_pve_editor.Rmd
editor comments reviews

##Modelled net seedling C uptake
The daily net C gain of seedlings (*G*), from @makela1997carbon, is given by

\
(1)
$$G(t) = L(P~\sigma - R)$$

where *L* is modelled total plant leaf area (m^2^), *P* is the daily C assimilation per unit leaf area (g C m^-2^ d^-1^, explained below), $\sigma$ is a self-shading parameter (explained below), and *R* is the mass based leaf respiration (g C d^-1^).

\
*P* was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (*J*~max~, *V*~cmax~, *R*~dark~ and *g*~1~) for each treatment and meteorological data from an onsite weather station. Values of *J*~max~ and *V*~cmax~ are mean estimates from AC~i~ curves over two measurement periods (explained above). *R*~dark~ was was estimated using Eq. (2) from ***Tjoekler 2008***, which was parameterized with a mean reference empircal measurement for each treatment, a Q~10~ value of 1.86 from a seperate experiment using the same tube stock seedlings and air temperature at each time step.

\
(2)
$$R~dark~ = R_{ref}Q_{10}~^{(T-T_{ref})/10}$$

The *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] to observed *g*~s~ values. Methods of the coupled leaf gas exchange model are also described in Duursma *et al.* [-@duursma2014peaked]. Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, leaf *A*~n~ rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment. *P* was calculated by converting predicted rates to mass C gain over 15 min time steps (g m^-2^) and then summed for 24 h. This resulted in 120 unique values of *P* for each soil volume treatment, one value for each day of the experiment. Thus, each daily time step for model runs included a value of *P* that represented both treatment specific photosynthetic parameters and meteorological constraints across the duration of the experiment.

>>>>

##Modelled net seedling C uptake
The daily total net C gain of seedlings (*G*), is given by

\
(1)
$$G(t) = \sigma LP_{day}$$

where $\sigma$ is a self-shading parameter, *L* is modelled total plant leaf area (m^2^), and  *P*~day~ is the net daily C assimilation per unit leaf area (g C m^-2).

\
*P* was predicted by using a coupled photosynthesis - stomatal conductance model [@farquhar1980biochemical;@medlyn2011reconciling] with the 'plantecophys' package [@duursma2015] in R with the mean photosynthetic parameters (*J*~max~, *V*~cmax~, *g*~1~ and *R*~dark~) for each treatment and meteorological data from an onsite weather station. Values of *J*~max~ and *V*~cmax~ are mean estimates from AC~i~ curves over two measurement periods (explained above). The *g*~1~ parameter was generated by fitting the optimal stomatal conductance model from [@medlyn2011reconciling] to observed *g*~s~ values. *R*~dark~ was was estimated using Eq. (2) from ***Tjoekler 2008***, which was parameterized with a mean reference empircal measurement for each treatment, a Q~10~ value of 1.86 from a seperate experiment using the same tube stock seedlings and air temperature at each time step.

\
(2)
$$R~dark~ = R_{ref}Q_{10}~^{(T-T_{ref})/10}$$
Methods of the coupled leaf gas exchange model are also described in Duursma *et al.* [-@duursma2014peaked]. Combined with the meteorological parameters; PPFD, air temperature, and relative humidity, at 15 min intervals, leaf *A*~n~ rates ($\mu$mol CO~2~ m^-2^ s^-1^) were then predicted for each soil volume treatment. *P*~day~ was calculated by converting predicted rates to mass C gain over 15 min time steps (g m^-2^) and then summed for 24 h. This resulted in 120 unique values of *P* for each soil volume treatment, one value for each day of the experiment. Thus, each daily time step for model runs included a value of *P*~day~ that represented both treatment specific photosynthetic parameters and meteorological constraints across the duration of the experiment.
